A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-02 paper/refactor.tex
some fixes for tables ordering and text typos on results

\input{handpicked_table}
\section{Results}
This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.

%\subsubsection{Top senses for selected works}
\input{results}

ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT ASDQWEQWEQWEQWEQ FILL THIS WITH SOME TEXT

%\subsubsection{Similarities with chosen concepts}
\input{results_sim_tables}

\newpage

\subsubsection{Observations}

>>>>

\input{handpicked_table}
\newpage

\section{Results}
This section is divided in two: first, we present the \textit{top senses} of the documents listed in ``Text corpus''; second, we present the similarities between the documents and the word-senses evaluation set.

\input{results}

In Top Senses table we can observe that some senses like local\_anesthetic was matched on Whats to be done? as first result. \\
Also in State and revolution Marx was matched with a United States comedian and a similar result we got with Berstein that was matched with a composer, however in the case of Engels it was matched to a socialist who wrote the Communist Manifesto with Karl Marx. \\
$Similarities$ tables shows that, in most of the works, synsets $lion$, $sugar$, $hair$, $car$ and $television\_receiver$ had a lower similarity in most of the works. \\
One strange result was $Hair$ that matched second in similarity score in Imperialism, the Highest St....

%\subsubsection{Similarities with chosen concepts}
\newpage
\input{results_sim_tables}
